---
title: "TJ_River_Alpha_Diversity"
output: html_notebook
---
```{r}
if (!require("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
```
```{r}
library(ggplot2)
library(ggpubr)
library(FSA)
library(dunn.test)
library(rstatix)
library(dplyr)
```
### Run Qiime2 alpha diversity metrics on Feature Table. In this case, we have observed features, pielou_evenness, and shannon_entropy. Last column should be metadata, in this case - sample site name.
### Import data
```{r}
alpha <- read.csv('./tj_river_alpha_diverity_qiime2.txt')
```
### Perform Dunn Test on features, evenness, and shannon
```{r}
attach(alpha)
```
```{r}
dunn_of_list <- dunn.test(observed_features, site, altp = TRUE, table = FALSE, list = TRUE)
dunn_of_df <- do.call(rbind.data.frame, dunn_of_list)
dunn_of_df_t <- as.data.frame(t(dunn_of_df))
dunn_of_df_t[, c(3)] <- sapply(dunn_of_df_t[, c(3)], as.numeric)
dunn_of_df_t$Rounded = round(dunn_of_df_t$V3,4)
```
```{r}
dunn_evenness_list <- dunn.test(evenness, site, altp = TRUE, table = FALSE, list = TRUE)
dunn_evenness_df <- do.call(rbind.data.frame, dunn_evenness_list)
dunn_evenness_df_t <- as.data.frame(t(dunn_evenness_df))
dunn_evenness_df_t[, c(3)] <- sapply(dunn_evenness_df_t[, c(3)], as.numeric)
dunn_evenness_df_t$Rounded = round(dunn_evenness_df_t$V3,4)
```
```{r}
dunn_shannon_list <- dunn.test(shannon, site, altp = TRUE, table = FALSE, list = TRUE)
dunn_shannon_df <- do.call(rbind.data.frame, dunn_shannon_list)
dunn_shannon_df_t <- as.data.frame(t(dunn_shannon_df))
dunn_shannon_df_t[, c(3)] <- sapply(dunn_shannon_df_t[, c(3)], as.numeric)
dunn_shannon_df_t$Rounded = round(dunn_shannon_df_t$V3,4)
```
### Create statistical results tables
```{r}
stat.test <- tibble::tribble(
  ~group1, ~group2, ~p,
  "Boca Rio", "Goat Canyon", 0,
  "Boca Rio", "Smuggler's Gulch", 0,
  "Goat Canyon", "Smuggler's Gulch", 0,
  "Boca Rio", "Stewart's Drain", 0,
  "Goat Canyon", "Stewart's Drain", 0,
  "Smuggler's Gulch", "Stewart's Drain", 0,
  "Boca Rio", "TJ Channel", 0,
  "Goat Canyon", "TJ Channel", 0,
  "Smuggler's Gulch", "TJ Channel", 0,
  "Stewart's Drain", "TJ Channel", 0,
  "Boca Rio", "Yogurt Canyon", 0,
  "Goat Canyon", "Yogurt Canyon", 0,
  "Smuggler's Gulch", "Yogurt Canyon", 0,
  "Stewart's Drain", "Yogurt Canyon", 0,
  "TJ Channel", "Yogurt Canyon", 0
)
stat.test_of <- stat.test
stat.test_of$p <- dunn_of_df_t$Rounded
stat.test_evenness <- stat.test
stat.test_evenness$p <- dunn_evenness_df_t$Rounded
stat.test_shannon <- stat.test
stat.test_shannon$p <- dunn_shannon_df_t$Rounded
```
### Create Observed Features Graph with statistical results
```{r}
#Observed Features at Sampling Site
my_comparisons_of <- list( c("Boca Rio", "Smuggler's Gulch"))
o_f_graph <- ggplot(alpha, aes(x=site, y=observed_features)) + theme_bw() + geom_boxplot(fill='white', lwd = 0.6) +
  labs(title="",x="",y="Observed Features") +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.4) + rotate_x_text(angle = 45) +
  theme(axis.text = element_text(face="bold", size = 9, colour = "grey20"),axis.title = element_text(face="bold", size=12),plot.title = element_text(face="bold"), panel.grid.major = element_line(size = 0.75, linetype = "solid")) + stat_pvalue_manual(
    stat.test_of, 
    y.position = 38500, step.increase = 0.1,
    label = "p",
    hide.ns = TRUE
    )
o_f_graph
```
### Create Evenness Graph with statistical results
```{r}
#Evenness at Sampling Site
even_graph <- ggplot(alpha, aes(x=site, y=evenness)) + theme_bw() + geom_boxplot(fill='white', lwd = 0.6) +
  labs(title="",x="",y="Evenness") +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.4) + rotate_x_text(angle = 45) +
  theme(axis.text = element_text(face="bold", size = 9, colour = "grey20"),axis.title = element_text(face="bold", size=12),plot.title = element_text(face="bold"), panel.grid.major = element_line(size = 0.75, linetype = "solid")) + stat_pvalue_manual(
    stat.test_evenness, 
    y.position = 0.46, step.increase = 0.1,
    label = "p",
    hide.ns = TRUE
    )
even_graph
```
### Create Shannon Index Graph with statistical results
```{r}
#Shannon Index at Sampling Site
s_i_graph <- ggplot(alpha, aes(x=site, y=shannon)) + theme_bw() + geom_boxplot(fill='white', lwd = 0.6) +
  labs(title="",x="",y="Shannon Index") +
  geom_dotplot(binaxis='y', stackdir='center', dotsize=0.4) + rotate_x_text(angle = 45) +
  theme(axis.text = element_text(face="bold", size = 9, colour = "grey20"), axis.title = element_text(face="bold", size=12),plot.title = element_text(face="bold"), panel.grid.major = element_line(size = 0.75, linetype = "solid")) + stat_pvalue_manual(
    stat.test_shannon, 
    y.position = 6.8, step.increase = 0.1,
    label = "p",
    hide.ns = TRUE
    )
s_i_graph
```
### Create Combined Plot
```{r}
all_alpha_graph <- ggarrange(o_f_graph,even_graph,s_i_graph,
                                    labels = c("A", "B", "C"),
                                    ncol = 3, nrow = 1)
all_alpha_graph
```
### Save Combined Plot
```{r}
ggsave('./tj_river_alpha_diverity_qiime2_all_alpha_graph.png',width=15, height=8, plot = all_alpha_graph)
```